---
title: "r_intro PS 2_answer"
author: "than Zaw Oo"
date: "2022-11-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



# Practice Summary Statistics with atomic vector 
library(tidyverse)

df<-iris

## for means_list_1, using a sample size 10 and replication time 100.
mean_list <- replicate(n = 100, expr = mean(sample(df$Sepal.Length,size = 10, replace=TRUE)))                    
# assign mean list as vector with 100 number                
names(mean_list)<- c(1:100)
print(mean_list)

##test as 100 times vector
test <- replicate(n = 100,     expr = mean(sample(df$Sepal.Length,size = 10,replace=TRUE)))
names(test)<- c(1:100)
rep(test, time=100)
print(test)
means_list_1 <- data.frame(cbind(test, mean_list))
means_list_1


##for means_list_2, using a sample size 30 and replication time 200.

mean_list <- replicate(n = 200, expr = mean(sample(df$Sepal.Length,size = 30, replace=TRUE)))                    
# assign mean list as vector with 200 number                
names(mean_list)<- c(1:200)
print(mean_list)



##test as 100 times vector
df<-iris
test <- replicate(n =200,     expr = mean(sample(df$Sepal.Length,size = 30,replace=TRUE)))
names(test)<- c(1:200)
rep(test, time=200)
print(test)
means_list_2 <- data.frame(cbind(test, mean_list))
means_list_2

##for means_list_3, using a sample size 50 and replication time 1,000

mean_list <- replicate(n =1000, expr = mean(sample(df$Sepal.Length,size =50, replace=TRUE)))                    
# assign mean list as vector with 1000 number                
names(mean_list)<- c(1:1000)
print(mean_list)

##test as 1000 times vector
df<-iris
test <- replicate(n =1000,     expr = mean(sample(df$Sepal.Length,size = 50,replace=TRUE)))
names(test)<- c(1:1000)
rep(test, time=1000)
print(test)
means_list_3 <- data.frame(cbind(test, mean_list))
means_list_3

###for means_list_4, using a sample size 50 and replication time 3,000


mean_list <- replicate(n =3000, expr = mean(sample(df$Sepal.Length,size =50, replace=TRUE)))                    
# assign mean list as vector with 3000 number                
names(mean_list)<- c(1:3000)
print(mean_list)

##test as 3000 times vector
df<-iris
test <- replicate(n =3000,     expr = mean(sample(df$Sepal.Length,size = 50,replace=TRUE)))
names(test)<- c(1:3000)
rep(test, time=3000)
print(test)
means_list_4 <- data.frame(cbind(test, mean_list))
means_list_4


##for means_list_5, using a sample size 50 and replication time 10,000

mean_list <- replicate(n =10000, expr = mean(sample(df$Sepal.Length,size =50, replace=TRUE)))                    
# assign mean list as vector with 10000 number                
names(mean_list)<- c(1:10000)
print(mean_list)

##test as 10000 times vector
df<-iris
test <- replicate(n =10000,     expr = mean(sample(df$Sepal.Length,size = 50,replace=TRUE)))
names(test)<- c(1:10000)
rep(test, time=10000)
print(test)
means_list_5 <- data.frame(cbind(test, mean_list))
means_list_5


##store 
means_seris <- rbind(means_list_1, means_list_2, means_list_3, means_list_4, means_list_5)

















Let's go back to the previous exercise on implementation of the sampling distribution of the means. 


2. Construct the list of 100 means values from the `Sepal.Length` and each mean value should construct from 10 sample sizes. (sample size = 10, replication 100 times)
2. Assigned the result (vector with 100 numbers) as vector name called `means_list` and . 
3. Construct the another vector called `test` and assigned `1` hundred time in that vector. Use `rep()` function for generation of same value for 100 times. 
4. Then, using `cbind` function to combined those two vectors" `test` and `mean_list`, and treat the result as `data.frame` and assigned to the object name `mean_list_1`. You can try with below demo code. 

```
means_list_1 <- data.frame(cbind(number, mean_list))

```

Repeat the same process from numbers 1 to 4, but using different sample size and replication number this time. 

+ for `means_list_2`, using a sample size 30 and replication time 200. 
+ for `means_list_3`, using a sample size 50 and replication time 1,000.  
+ for `means_list_4`, using a sample size 50 and replication time 3,000.  
+ for `means_list_5`, using a sample size 50 and replication time 10,000.  


This time, we are going to create the list to store all those `means_list_x` (where `x` `1:5`) and assigned that list as `means_seris`. 
And, perform the following function from that list. 

1. calculate the mean of `means_list_x` (where `x` `1:5`) from that list (using the command related to filtering list from lecture 2. 

For example, if we use the following command, we can get the first dataframe. You work is to calculate the mean value of column `mean_list`. 

```
means_seris[[1]]
```

2. Using `bind_rows()` function to combined all dataset from `means_seris` and assigned into object called `df_means_combined`. Please make sure that your result dataset should have `16100` observations and 2 variables; `test` and `mean_list`. 

3. Finally, calculate the mean value for each group of `test` using following example. In this exercise, we are going to use `group_by` function from the `tidyverse` packge and `%>%` operator (pipe operator). 

```{r, message = FALSE}
library(tidyverse)

iris %>%
  group_by(Species) %>%
  summarise(mean = mean(Sepal.Length))

```
